---
title: "SQL50-with R and MySQL"
author: "Bonnie Yuan"
date: "2025-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("dplyr")
library(dplyr)
```

## 1757. Recyclable and Low Fat Products

```{sql}
select product_id
from Products
where low_fats='Y'
and recyclable='Y';
```

```{r}
# Create the Products data frame
Products <- data.frame(
  product_id = c(0, 1, 2, 3, 4),
  low_fats = c('Y', 'Y', 'N', 'Y', 'N'),
  recyclable = c('N', 'Y', 'Y', 'Y', 'N')
)
# Filter products that are both low fat and recyclable
result <- Products %>% 
  filter(low_fats=='Y' &recyclable=='Y' ) %>% 
  dplyr::select(product_id)

# Display the result
print(result)

```

## 584. Find Customer Referee
Find the names of the customer that are not referred by the customer with id = 2.

Return the result table in any order.



```{sql}
select name
from Customer
where referee_id is null
or referee_id!=2;

```

```{r}
library(dplyr)

# Create the Customer data frame
Customer <- data.frame(
  id = c(1, 2, 3, 4, 5, 6),
  name = c('Will', 'Jane', 'Alex', 'Bill', 'Zack', 'Mark'),
  referee_id = c(NA, NA, 2, NA, 1, 2)
)
results<-Customer %>% 
  filter(referee_id !=2 | is.na(referee_id)) %>% 
  dplyr::select(name)
print(results)

```
## 595. Big Countries

A country is big if:

it has an area of at least three million (i.e., 3000000 km2), or
it has a population of at least twenty-five million (i.e., 25000000).
Write a solution to find the name, population, and area of the big countries.

Return the result table in any order.

The result format is in the following example.

```{sql}
select name, population,area
from World
where area>3000000
or population<25000000;

```

```{r}
library(dplyr)

# Create the World data frame
World <- data.frame(
  name = c('Afghanistan', 'Albania', 'Algeria', 'Andorra', 'Angola'),
  continent = c('Asia', 'Europe', 'Africa', 'Europe', 'Africa'),
  area = c(652230, 28748, 2381741, 468, 1246700),
  population = c(25500100, 2831741, 37100000, 78115, 20609294),
  gdp = c(20343000000, 12960000000, 188681000000, 3712000000, 100990000000)
)

result <- World %>%
  filter(area >= 3000000 | population >= 25000000) %>%
  select(name, population, area)
print(results)

```

## 1148. Article Views I

Write a solution to find all the authors that viewed at least one of their own articles.

Return the result table sorted by id in ascending order.

```{sql}
select distinct author_id as id
from Views
where author_id = viewer_id
order by 1 asc;
```

```{r}
library(dplyr)

# Create the Views data frame
Views <- data.frame(
  article_id = c(1, 1, 2, 2, 4, 3, 3),
  author_id = c(3, 3, 7, 7, 7, 4, 4),
  viewer_id = c(5, 6, 7, 6, 1, 4, 4),
  view_date = as.Date(c('2019-08-01', '2019-08-02', '2019-08-01', '2019-08-02', '2019-07-22', '2019-07-21', '2019-07-21'))
)

results<-Views %>% 
  filter(author_id ==viewer_id) %>% 
  dplyr:: select(author_id) %>% 
  distinct() %>% 
  rename(id=author_id) %>% 
  arrange(id)
print(results)
```

## 1683. Invalid Tweets
Write a solution to find the IDs of the invalid tweets. The tweet is invalid if the number of characters used in the content of the tweet is strictly greater than 15.

Return the result table in any order.
```{sql}
select tweet_id
from Tweets
where char_length(content)>15;

```

```{r}
library(dplyr)

# Create the Tweets data frame
Tweets <- data.frame(
  tweet_id = c(1, 2),
  content = c("Let us Code", "More than fifteen chars are here!")
)

results<-Tweets %>% 
  filter(nchar(content)>15) %>% 
  select(tweet_id)

print(results)
```

## 1378. Replace Employee ID With The Unique Identifier
Write a solution to show the unique ID of each user, If a user does not have a unique ID replace just show null.

Return the result table in any order.

```{sql}
select em.unique_id, e.name
from Employees e
left join EmployeeUNI em
on e.id=em.id;
```
```{r}

# Create Employees data frame
Employees <- data.frame(
  id = c(1, 7, 11, 90, 3),
  name = c('Alice', 'Bob', 'Meir', 'Winston', 'Jonathan')
)

# Create EmployeeUNI data frame
EmployeeUNI <- data.frame(
  id = c(3, 11, 90),
  unique_id = c(1, 2, 3)
)

results<-Employees %>% 
  left_join(EmployeeUNI,by='id') %>% 
  select(unique_id,name)
results$unique_id [is.na(results$unique_id)]<-'null'
print(results)
```
## 1068. Product Sales Analysis I

Write a solution to report the product_name, year, and price for each sale_id in the Sales table.

Return the resulting table in any order.


```{sql}
select p.product_name, s.year,s.price
from Sales s
left join Product p
on s.product_id=p.product_id

```

```{r}
Sales <- data.frame(
  sale_id = c(1, 2, 7),
  product_id = c(100, 100, 200),
  year = c(2008, 2009, 2011),
  quantity = c(10, 12, 15),
  price = c(5000, 5000, 9000)
)
Product <- data.frame(
  product_id = c(100, 200, 300),
  product_name = c('Nokia', 'Apple', 'Samsung')
)
result<- Sales %>% 
  left_join(Product,by="product_id") %>% 
  select(product_name,year,price)
print(result)

```

## 1581. Customer Who Visited but Did Not Make Any Transactions

Write a solution to find the IDs of the users who visited without making any transactions and the number of times they made these types of visits.

Return the result table sorted in any order.



```{sql}

select customer_id,
count(*) as count_no_trans
from Visits
where visit_id not in (
select distinct visit_id
from Transactions
)
group by customer_id;
```



```{r}
library(dplyr)

# Create Visits data frame
Visits <- data.frame(
  visit_id = c(1, 2, 4, 5, 6, 7, 8),
  customer_id = c(23, 9, 30, 54, 96, 54, 54)
)

# Create Transactions data frame
Transactions <- data.frame(
  transaction_id = c(2, 3, 9, 12, 13),
  visit_id = c(5, 5, 5, 1, 2),
  amount = c(310, 300, 200, 910, 970)
)

results<-Visits %>% 
  anti_join(Transactions,by='visit_id') %>% 
  group_by(customer_id) %>% 
  summarize(count_no_trans = n(),.groups = 'drop') %>% 
  arrange(desc(count_no_trans))
print(results)
```
## **197. Rising Temperature**

Write a solution to find all dates' id with higher temperatures compared to its previous dates (yesterday).

Return the result table in any order.

```{sql}
select today.id
from weather yesterday
CROSS JOIN weather today
where datediff(today.recordDate,yesterday.recordDate)=1
and today.tempreture>yesterday.tempreture;
```





```{sql}
select id
from(
select id,
lag(temperature,1,null) over(
order by recordDate
) as prev_temp
from Weather
) t
where prev_temp<temperature 
and prev_temp is not null


```

```{r}
library(dplyr)

# Create Weather data frame
Weather <- data.frame(
  id = c(1, 2, 3, 4),
  recordDate = as.Date(c('2015-01-01', '2015-01-02', '2015-01-03', '2015-01-04')),
  temperature = c(10, 25, 20, 30)
)

results<-Weather %>% 
  arrange(recordDate) %>% 
  mutate(prev_temp = lag(temperature)) %>% 
  filter(temperature>prev_temp&!is.na(prev_temp)) %>% 
  select(id)

print(results)

```

## **1661. Average Time of Process per Machine**

```{sql}
with out_dat as(
SELECT machine_id, process_id, 
max(CASE WHEN activity_type = 'start' THEN timestamp END) as start_time,
max(CASE WHEN activity_type = 'end' THEN timestamp END)as end_time
from Activity
GROUP BY machine_id, process_id
)
select machine_id,
round(avg(end_time-start_time),3) as processing_time
from out_dat
group by machine_id


```

Note:
If you just use CASE without aggregation (`MAX()`), SQL will try to produce something like:

+------------+------------+------------+----------+
| machine_id | process_id | start_time | end_time |
+------------+------------+------------+----------+
| 0          | 0          | 0.712      | NULL     |
| 0          | 0          | NULL       | 1.520    |
| 0          | 1          | 3.140      | NULL     |
| 0          | 1          | NULL       | 4.120    |
+------------+------------+------------+----------+
This doesn't work because start_time and end_time appear on separate rows instead of the same row.





```{r}
library(dplyr)

# Create Activity data frame
Activity <- data.frame(
  machine_id = c(0, 0, 0, 0, 1, 1, 1, 1, 2, 2, 2, 2),
  process_id = c(0, 0, 1, 1, 0, 0, 1, 1, 0, 0, 1, 1),
  activity_type = c('start', 'end', 'start', 'end', 'start', 'end', 'start', 'end', 'start', 'end', 'start', 'end'),
  timestamp = c(0.712, 1.520, 3.140, 4.120, 0.550, 1.550, 0.430, 1.420, 4.100, 4.512, 2.500, 5.000)
)
results<-Activity %>% 
  group_by(machine_id,process_id) %>% 
  summarise(start_time=timestamp[activity_type=='start'],
         end_time = timestamp[activity_type=='end'],.groups='drop') %>% 
  mutate(processing_time=end_time-start_time) %>% 
  group_by(machine_id) %>% 
  summarise(processing_time=round(mean(processing_time),3))

print(results)
```

## 577. Employee Bonus

Write a solution to report the name and bonus amount of each employee with a bonus less than 1000.

Return the result table in any order.

```{sql}
select e.name, b.bonus
from Employee e
left join Bonus b 
on e.empId = b.empId
where b.bonus is null or b.bonus < 1000;
```

```{r}
Employee <- data.frame(
  empId = c(3, 1, 2, 4),
  name = c("Brad", "John", "Dan", "Thomas"),
  supervisor = c(NA, 3, 3, 3),
  salary = c(4000, 1000, 2000, 4000)
)

Bonus <- data.frame(
  empId = c(2, 4),
  bonus = c(500, 2000)
)

Employee %>% 
  left_join(Bonus,by='empId') %>% 
  filter(bonus<1000 | is.na(bonus)) %>% 
  select(name, bonus)
```


## **1280. Students and Examinations**

```{sql}
with full_sub as (
select s.student_id, s.student_name, sub.subject_name
from Students s
cross join Subjects sub
),
counts as(
select *,
count(*) as attended_exams
from Examinations
group by student_id,subject_name
)
select f.student_id, f.student_name,f.subject_name,if.null(c.attended_exams,0) as attended_exams
from full_sub f
left join counts c 
on f.student_id=c.student_id and f.subject_name=c.subject_name
order by student_id, subject_name
```


```{r}
library(dplyr)

# Create Students data frame
Students <- data.frame(
  student_id = c(1, 2, 13, 6),
  student_name = c('Alice', 'Bob', 'John', 'Alex')
)

# Create Subjects data frame
Subjects <- data.frame(
  subject_name = c('Math', 'Physics', 'Programming')
)

# Create Examinations data frame
Examinations <- data.frame(
  student_id = c(1, 1, 1, 2, 1, 1, 13, 13, 13, 2, 1),
  subject_name = c('Math', 'Physics', 'Programming', 'Programming', 'Physics', 'Math', 'Math', 'Programming', 'Physics', 'Math', 'Math')
)

full_dat<-Students %>% 
  cross_join(Subjects)

counts<-Examinations %>% 
  group_by(student_id,subject_name) %>% 
  summarise(attended_exams = n(),.groups='drop')

full_dat %>% 
  left_join(counts,by=c('student_id', 'subject_name')) %>% 
  mutate(attended_exams=ifelse(is.na(attended_exams),0,attended_exams)) %>% 
    arrange(student_id, subject_name)
```

## **570. Managers with at Least 5 Direct Reports**

Write a solution to find managers with at least five direct reports.

Return the result table in any order.


```{sql}
select name
from Employee
where id in (
select managerId
from Employee
group by managerId
having count(*) >=5
)
```

```{sql}
with counts as (
    select *, count(managerId) as counts
    from Employee
    group by managerId
)

select e.name
from Employee e
inner join counts c
on e.id=c.managerId
where c.counts >=5 and c.counts is not null
```

```{r}
Employee <- data.frame(
  id = c(101, 102, 103, 104, 105, 106),
  name = c("John", "Dan", "James", "Amy", "Anne", "Ron"),
  department = c("A", "A", "A", "A", "A", "B"),
  managerId = c(NA, 101, 101, 101, 101, 101)
)

managers<-Employee %>%
  group_by(managerId) %>% 
  summarise(counts = n()) %>% 
  filter(counts>=5) 
Employee %>% 
  filter(id %in% managers$managerId) %>% 
  select(name)
```


## 1934. Confirmation Rate

The confirmation rate of a user is the number of 'confirmed' messages divided by the total number of requested confirmation messages. The confirmation rate of a user that did not request any confirmation messages is 0. Round the confirmation rate to two decimal places.

Write a solution to find the confirmation rate of each user.

Return the result table in any order.

```{sql}
select s.user_id, 
round(ifnull(avg(c.action='confirmed'),0),2) as confirmation_rate
from Signups s
left join Confirmations c
on s.user_id=c.user_id
group by user_id
```

```{r}

library(dplyr)

# Create Signups data frame
Signups <- data.frame(
  user_id = c(3, 7, 2, 6),
  time_stamp = as.POSIXct(c('2020-03-21 10:16:13', '2020-01-04 13:57:59', '2020-07-29 23:09:44', '2020-12-09 10:39:37'))
)

# Create Confirmations data frame
Confirmations <- data.frame(
  user_id = c(3, 3, 7, 7, 7, 2, 2),
  time_stamp = as.POSIXct(c('2021-01-06 03:30:46', '2021-07-14 14:00:00', '2021-06-12 11:57:29', '2021-06-13 12:58:28', '2021-06-14 13:59:27', '2021-01-22 00:00:00', '2021-02-28 23:59:59')),
  action = c('timeout', 'timeout', 'confirmed', 'confirmed', 'confirmed', 'confirmed', 'timeout')
)

confirmation_rate<-Confirmations %>% 
  group_by(user_id) %>% 
  summarise(confirmation_rate =round( mean(action=='confirmed'),2))
  
confirmation_rate

Signups %>%
  left_join(confirmation_rate, by = 'user_id') %>%
  mutate(
    confirmation_rate = ifelse(is.na(confirmation_rate), 0, confirmation_rate)
  ) %>%
  select(user_id, confirmation_rate)


result

```
## 620. Not Boring Movies
Write a solution to report the movies with an odd-numbered ID and a description that is not "boring".

Return the result table ordered by rating in descending order.

```{sql}
select *
from Cinema
where description!='boring' & id%2!=0
order by rating desc;

```

```{r}
Cinema <- data.frame(
  id = c(1, 2, 3, 4, 5),
  movie = c("War", "Science", "irish", "Ice song", "House card"),
  description = c("great 3D", "fiction", "boring", "Fantacy", "Interesting"),
  rating = c(8.9, 8.5, 6.2, 8.6, 9.1)
)

Cinema %>% 
  filter(description!='boring' & id %% 2!= 0) %>% 
  arrange(desc(rating))
```

## 1251. Average Selling Price

```{sql}
select p.product_id, round(ifnull(sum(p.price*u.units)/sum(u.units),0),2) as average_price
from Prices p
left join UnitsSold u
on p.product_id = u.product_id
and u.purchase_date between p.start_date and p.end_date
group by product_id
```

```{r}

# Create Prices data frame
Prices <- data.frame(
  product_id = c(1, 1, 2, 2),
  start_date = as.Date(c('2019-02-17', '2019-03-01', '2019-02-01', '2019-02-21')),
  end_date = as.Date(c('2019-02-28', '2019-03-22', '2019-02-20', '2019-03-31')),
  price = c(5, 20, 15, 30)
)

# Create UnitsSold data frame
UnitsSold <- data.frame(
  product_id = c(1, 1, 2, 2),
  purchase_date = as.Date(c('2019-02-25', '2019-03-01', '2019-02-10', '2019-03-22')),
  units = c(100, 15, 200, 30)
)

UnitsSold %>% 
  left_join(Prices,by='product_id') %>% 
  filter(purchase_date<=end_date& purchase_date>=start_date) %>% 
  group_by(product_id) %>% 
  summarise(average_price = round(sum(price*units)/sum(units),2))
```


## 1075. Project Employees I

reports the average experience years of all the employees for each project, rounded to 2 digits.

Return the result table in any order.

Output: 
+-------------+---------------+
| project_id  | average_years |
+-------------+---------------+
| 1           | 2.00          |
| 2           | 2.50          |
+-------------+---------------+

```{sql}
select p.project_id, round(avg(experience_years),2) as average_years
from Project p 
left join Employee e
on p.employee_id = e.employee_id
group by project_id
```


```{r}
library(dplyr)

# Create Project data frame
Project <- data.frame(
  project_id = c(1, 1, 1, 2, 2),
  employee_id = c(1, 2, 3, 1, 4)
)

# Create Employee data frame
Employee <- data.frame(
  employee_id = c(1, 2, 3, 4),
  name = c('Khaled', 'Ali', 'John', 'Doe'),
  experience_years = c(3, 2, 1, 2)
)

Project %>%
  left_join(Employee, by = 'employee_id') %>%
  group_by(project_id) %>%
  summarise(average_years = round(mean(experience_years), 2), .groups = 'drop')

```

## 1633. Percentage of Users Attended a Contest

Write a solution to find the percentage of the users registered in each contest rounded to two decimals.

Return the result table ordered by percentage in descending order. In case of a tie, order it by contest_id in ascending order.

```{sql}
select contest_id,
round(count(distinct user_id)/(select count(*) from Users )*100,2) as percentage
from Register 
group by contest_id
order by percentage desc,contest_id;
```

```{r}

Users <- data.frame(
  user_id = c(6, 2, 7),
  user_name = c('Alice', 'Bob', 'Alex')
)

Register <- data.frame(
  contest_id = c(215, 209, 208, 210, 208, 209, 209, 215, 208, 210, 207, 210),
  user_id = c(6, 2, 2, 6, 6, 7, 6, 7, 7, 2, 2, 7)
)

# Count the number of unique users
total_users <- Users %>% 
  distinct(user_id) %>% 
  summarise(tot=n())

Register %>%
  group_by(contest_id) %>%
  summarise(registered_users = n(), .groups = 'drop') %>%
  mutate(percentage = round((registered_users / total_users$tot) * 100, 2)) %>%
  arrange(desc(percentage), contest_id)

```

## 1211. Queries Quality and Percentage

Write a solution to find each query_name, the quality and poor_query_percentage.

Both quality and poor_query_percentage should be rounded to 2 decimal places.

Return the result table in any order.

```{sql}


select query_name,
round(avg(rating/position),2) as quality,
round(avg(rating<3)*100,2) as poor_query_percentage
from Queries
group by query_name
```


```{r}
Queries <- data.frame(
  query_name = c('Dog', 'Dog', 'Dog', 'Cat', 'Cat', 'Cat'),
  result = c('Golden Retriever', 'German Shepherd', 'Mule', 'Shirazi', 'Siamese', 'Sphynx'),
  position = c(1, 2, 200, 5, 3, 7),
  rating = c(5, 5, 1, 2, 3, 4)
)

# Calculate quality and poor query percentage
Queries %>% 
  group_by(query_name) %>% 
  summarise(quality = round(mean(rating/position),2),
            poor_query_percentage = round(mean(rating<3)*100,2))

```

## 1193. Monthly Transactions I

Write an SQL query to find for each month and country, the number of transactions and their total amount, the number of approved transactions and their total amount.

Return the result table in any order.
```{sql}
select LEFT(trans_date, 7) AS month, country,
count(*) as trans_count,
sum(state='approved') as approved_count,
sum(amount) as trans_total_amount,
sum(if(state='approved',amount,0)) as approved_total_amount
from Transactions
group by 1,2

```

```{r}
Transactions <- data.frame(
  id = c(121, 122, 123, 124),
  country = c("US", "US", "US", "DE"),
  state = c("approved", "declined", "approved", "approved"),
  amount = c(1000, 2000, 2000, 2000),
  trans_date = as.Date(c("2018-12-18", "2018-12-19", "2019-01-01", "2019-01-07"))
)

Transactions %>% 
  mutate(month = format(trans_date,'%Y-%m')) %>% 
  group_by(month,country) %>% 
  summarise(
    trans_count = n(),
    approved_count = sum(state=='approved'),
    trans_total_amount = sum(amount),
    approved_total_amount = sum(amount[state=='approved'])
  )

```

## 1174. Immediate Food Delivery II

```{sql}
select round(avg(order_date=customer_pref_delivery_date)*100,2)as immediate_percentage
from Delivery
where ( customer_id,order_date)in (
select customer_id,min(order_date)
from Delivery
group by customer_id
)

```

```{r}

Delivery <- data.frame(
  delivery_id = c(1, 2, 3, 4, 5, 6, 7),
  customer_id = c(1, 2, 1, 3, 3, 2, 4),
  order_date = as.Date(c('2019-08-01', '2019-08-02', '2019-08-11', '2019-08-24', '2019-08-21', '2019-08-11', '2019-08-09')),
  customer_pref_delivery_date = as.Date(c('2019-08-02', '2019-08-02', '2019-08-12', '2019-08-24', '2019-08-22', '2019-08-13', '2019-08-09'))
)


Delivery %>% 
  group_by(customer_id) %>% 
  filter(order_date == min(order_date)) %>% 
  ungroup() %>% 
  summarise(tot = n(),immediate_order = sum(order_date==customer_pref_delivery_date)) %>% 
  mutate(immediate_percentage = round(immediate_order /tot*100, 2))%>%
  select(immediate_percentage)

```
## **550. Game Play Analysis IV**

Write a solution to report the fraction of players that logged in again on the day after the day they first logged in, rounded to 2 decimal places. In other words, you need to count the number of players that logged in for at least two consecutive days starting from their first login date, then divide that number by the total number of players.


```{sql}
select round(count(player_id)/(select count(distinct player_id) from Activity),2) as fraction
from Activity 
where (player_id,DATE_SUB(event_date, INTERVAL 1 DAY)) in (
select player_id, min(event_date)
from Activity
group by player_id
);

```


```{r}
Activity <- data.frame(
  player_id = c(1, 1, 2, 3, 3),
  device_id = c(2, 2, 3, 1, 4),
  event_date = as.Date(c('2016-03-01', '2016-03-02', '2017-06-25', '2016-03-02', '2018-07-03')),
  games_played = c(5, 6, 1, 0, 5)
)

num<-Activity %>% 
  group_by(player_id) %>% 
  filter(event_date==min(event_date)+1) %>% 
  summarise(num = n(),.groups = 'drop') %>% 
  pull(num)

# Check if player logged in the day after their first login
tot_login <- Activity %>%
  distinct(player_id) %>% 
summarise(num = n(),.groups = 'drop') %>% 
  pull(num)

# Calculate fraction
fraction <- round(num /tot_login, 2)

# Create result data frame
result <- data.frame(fraction = fraction)
print(result)
```

## 2356. Number of Unique Subjects Taught by Each Teacher
Write a solution to calculate the number of unique subjects each teacher teaches in the university.

Return the result table in any order.
```{sql}
select teacher_id, count( distinct subject_id) as cnt
from Teacher
group by teacher_id
```

```{r}
Teacher <- data.frame(
  teacher_id = c(1, 1, 1, 2, 2, 2, 2),
  subject_id = c(2, 2, 3, 1, 2, 3, 4),
  dept_id = c(3, 4, 3, 1, 1, 1, 1)
)
Teacher %>% 
  group_by(teacher_id) %>% 
  distinct(subject_id) %>% 
  summarise(cnt=n(),.groups='drop')
  
```


## 1141. User Activity for the Past 30 Days I
Write a solution to find the daily active user count for a period of 30 days ending 2019-07-27 inclusively. A user was active on someday if they made at least one activity on that day.

Return the result table in any order.

```{sql}
select activity_date as day,
count(distinct user_id) as active_users
from Activity
where DATEDIFF('2019-07-27',activity_date)< 30
and DATEDIFF('2019-07-27', activity_date)>=0
group by 1
```

```{r}

# Creating Activity table
Activity <- data.frame(
  user_id = c(1, 1, 1, 2, 2, 2, 3, 3, 3, 4, 4),
  session_id = c(1, 1, 1, 4, 4, 4, 2, 2, 2, 3, 3),
  activity_date = as.Date(c(
    "2019-07-20", "2019-07-20", "2019-07-20",
    "2019-07-20", "2019-07-21", "2019-07-21",
    "2019-07-21", "2019-07-21", "2019-07-21",
    "2019-06-25", "2019-06-25")),
  activity_type = c(
    "open_session", "scroll_down", "end_session",
    "open_session", "send_message", "end_session",
    "open_session", "send_message", "end_session",
    "open_session", "end_session")
)

Activity %>%   
  filter(activity_date >= as.Date("2019-07-27")-30 & activity_date <= as.Date("2019-07-27")) %>% 
  group_by(activity_date) %>% 
  distinct(user_id) %>% 
  summarise(active_users = n())
```

## 1070. Product Sales Analysis III

Write a solution to select the product id, year, quantity, and price for the first year of every product sold.

Return the resulting table in any order.

```{sql}
select product_id, year as first_year, quantity, price
from Sales
where (product_id, year) in (
select product_id,min(year)
from Sales
group by product_id
);
```


```{r}
Sales <- data.frame(
  sale_id = c(1, 2, 7),
  product_id = c(100, 100, 200),
  year = c(2008, 2009, 2011),
  quantity = c(10, 12, 15),
  price = c(5000, 5000, 9000)
)


Sales %>%
  group_by(product_id) %>%
  filter(year == min(year)) %>%
  select(product_id, first_year = year, quantity, price) %>%
  ungroup()



```

## 596. Classes More Than 5 Students

Write a solution to find all the classes that have at least five students.

Return the result table in any order.

```{sql}
select class
from Courses
group by class
having count(student)>=5
```

```{r}
Courses <- data.frame(
  student = c("A", "B", "C", "D", "E", "F", "G", "H", "I"),
  class = c("Math", "English", "Math", "Biology", "Math", 
            "Computer", "Math", "Math", "Math")
)

Courses %>% 
  group_by(class) %>% 
  summarise(num=n()) %>% 
  filter(num>=5)%>% 
  select(class)
  
```

## 1729. Find Followers Count

Write a solution that will, for each user, return the number of followers.

Return the result table ordered by user_id in ascending order.

```{sql}
select user_id,
 count(*) as followers_count
from Followers
group by user_id
order by user_id asc;
```


```{r}
Followers <- data.frame(
  user_id = c(0, 1, 2, 2),
  follower_id = c(1, 0, 0, 1)
)
Followers %>% 
  group_by(user_id) %>% 
  summarise(followers_count = n()) %>% 
  arrange(user_id)
```
## 619. Biggest Single Number. --subset use where ...in...
A single number is a number that appeared only once in the MyNumbers table.

Find the largest single number. If there is no single number, report null.

```{sql}
select max(num) as num 
from MyNumbers
where num in (
select max(num)
from MyNumbers
group by num
having count(num)=1
)

```

```{r}
MyNumbers <- data.frame(
  num = c(8, 8, 3, 3, 1, 4, 5, 6) # Example 1 input
)

MyNumbers <- data.frame(
  num = c(8, 8, 7, 7, 3, 3, 3) # Example 2 input
)

MyNumbers %>% 
  group_by(num) %>% 
  summarise(totnum = n(),.groups='drop') %>% 
  filter(totnum ==1) %>% 
  summarise(num = ifelse(n() > 0, max(num), NA))

```


## 1045. Customers Who Bought All Products

Write a solution to report the customer ids from the Customer table that bought all the products in the Product table.

Return the result table in any order.

```{sql}
select customer_id
from Customer
group by customer_id
having count(distinct product_key) = (select count(product_key) from Product)
```



```{r}
Customer <- data.frame(
  customer_id = c(1, 2, 3, 3, 1),
  product_key = c(5, 6, 5, 6, 6)
)
# Creating Product table
Product <- data.frame(
  product_key = c(5, 6)
)

Customer %>% 
  group_by(customer_id) %>% 
  distinct(product_key) %>% 
  summarise(numkey=n(),.groups = 'drop') %>% 
  filter(numkey == nrow(Product)) %>% 
  select(customer_id)


```

## 1731. The Number of Employees Which Report to Each Employee
For this problem, we will consider a manager an employee who has at least 1 other employee reporting to them.

Write a solution to report the ids and the names of all managers, the number of employees who report directly to them, and the average age of the reports rounded to the nearest integer.

Return the result table ordered by employee_id.
```{sql}
with manager as (
select *,count(*) as reports_count,round(avg(age)) as average_age
from Employees
group by reports_to
)
select e.employee_id,e.name, m.reports_count,m.average_age
from Employees e
inner join manager m
on e.employee_id=m.reports_to
order by employee_id

```


```{r}
Employees <- data.frame(
  employee_id = c(9, 6, 4, 2),
  name = c("Hercy", "Alice", "Bob", "Winston"),
  reports_to = c(NA, 9, 9, NA),
  age = c(43, 41, 36, 37)
)

# round() uses  "round to even" rule (also known as bankers' rounding)
Employees %>% 
  group_by(reports_to) %>% 
  summarise(reports_count=n(),
            average_age = round(mean(age)+0.01)) %>% 
  inner_join(Employees,by=c('reports_to'='employee_id')) %>% 
  select(employee_id=reports_to,name,reports_count,average_age)
```
## 1789. Primary Department for Each Employee

Employees can belong to multiple departments. When the employee joins other departments, they need to decide which department is their primary department. Note that when an employee belongs to only one department, their primary column is 'N'.

Write a solution to report all the employees with their primary department. For employees who belong to one department, report their only department.

Return the result table in any order.

```{sql}
select employee_id, department_id
from Employee
where primary_flag ='Y' or employee_id in (
select employee_id
from Employee
group by employee_id
having count(employee_id)=1
)
```

```{r}

Employee <- data.frame(
  employee_id = c(1, 2, 2, 3, 4, 4, 4),
  department_id = c(1, 1, 2, 3, 2, 3, 4),
  primary_flag = c("N", "Y", "N", "N", "N", "Y", "N")
)

Employee %>% 
  group_by(employee_id) %>% 
  filter(primary_flag=='Y' | n()==1) %>% 
  select(employee_id, department_id) %>%
  ungroup()
```
## 610. Triangle Judgement
Report for every three line segments whether they can form a triangle.

Return the result table in any order.

```{sql}
select *, 
case 
when x+y>z and x+z>y and y+z>x then 'Yes'
else 'No'
end as triangle 
from Triangle

```

```{r}
Triangle <- data.frame(
  x = c(13, 10),
  y = c(15, 20),
  z = c(30, 15)
)

Triangle %>% 
  mutate(triangle = ifelse(x+y>z&x+z>x&y+z>x,'Yes','No'))
```

## **180. Consecutive Numbers**

Find all numbers that appear at least three times consecutively.

Return the result table in any order.

```{sql}
select 
from Logs l1,
Logs l2,
Logs l3
where l1.id=l2.id-1
and l2.id=l3.id-1
and l1.num=l2.num
and l2.num=l3.num
```

```{r}
# Create Logs data frame
Logs <- data.frame(
  id = c(1, 2, 3, 4, 5, 6, 7),
  num = c(1, 1, 1, 2, 1, 2, 2)
)

Logs %>% 
  mutate(consecutive_group = cumsum(num!=lag(num,default = first(num)))) %>% 
  group_by(consecutive_group) %>% 
  filter(n()>=3) %>% 
  ungroup() %>% 
  select(ConsecutiveNums = num) %>%
  distinct()

# OR

Logs %>%
  mutate(consecutive_group = cumsum(num != lag(num, default = first(num)))) %>%
  group_by(consecutive_group, num) %>%
  summarise(count = n(), .groups = 'drop') %>%
  filter(count >= 3) %>%
  select(ConsecutiveNums = num) %>%
  distinct()

```
## 1164. Product Price at a Given Date

Write a solution to find the prices of all products on 2019-08-16. Assume the price of all products before any change is 10.

Return the result table in any order.


```{sql}
select product_id, 10 as price
from Products
group by product_id
having min(change_date) > '2019-08-16'
union
select product_id, new_price as price
from Products
where (product_id,change_date) in (
select product_id,max(change_date)
from Products
where change_date<='2019-08-16'
group by product_id
)
```


```{r}
library(dplyr)
# Create Products data frame
Products <- data.frame(
  product_id = c(1, 2, 1, 1, 2, 3),
  new_price = c(20, 50, 30, 35, 65, 20),
  change_date = as.Date(c('2019-08-14', '2019-08-14', '2019-08-15', '2019-08-16', '2019-08-17', '2019-08-18'))
)

# Find prices of all products on 2019-08-16
price_10 <- Products %>%
  group_by(product_id) %>% 
  filter(min(change_date)>as.Date('2019-08-16')) %>% 
  mutate(price=10)%>% 
  ungroup() %>%
  select(product_id, price)
  
price_other<-Products %>%
  group_by(product_id) %>% 
  filter(change_date<=as.Date('2019-08-16') ) %>% 
  slice_max(change_date, n = 1) %>% 
  ungroup() %>%
  select(product_id, price = new_price)


result <- rbind(price_other,price_10)
print(result)
```

## 1204. Last Person to Fit in the Bus

There is a queue of people waiting to board a bus. However, the bus has a weight limit of 1000 kilograms, so there may be some people who cannot board.

Write a solution to find the person_name of the last person that can fit on the bus without exceeding the weight limit. The test cases are generated such that the first person does not exceed the weight limit.

Note that only one person can board the bus at any given turn.

```{sql}
with sum_wt as(
select *,
sum(weight) over (order by turn) as sum_wt
from Queue
)
select person_name
from sum_wt
where sum_wt<=1000
order by turn desc
limit 1
```


```{r}
Queue <- data.frame(
  person_id = c(5, 4, 3, 6, 1, 2),
  person_name = c('Alice', 'Bob', 'Alex', 'John Cena', 'Winston', 'Marie'),
  weight = c(250, 175, 350, 400, 500, 200),
  turn = c(1, 5, 2, 3, 6, 4)
)

# Determine the last person who can fit on the bus without exceeding 1000 kg
result <- Queue %>%
  arrange(turn) %>%
  mutate(cumulative_weight = cumsum(weight)) %>%
  filter(cumulative_weight <= 1000) %>%
  slice_tail(n = 1) %>%
  select(person_name)

# Display the result
print(result)
```
##

```{sql}
select "Low Salary" as category,
sum(CASE WHEN income < 20000 THEN 1 ELSE 0 END)AS accounts_count
from Accounts
union 
select "Average Salary" as category,
sum(CASE WHEN income >= 20000 and income<=50000 THEN 1 ELSE 0 END)AS accounts_count
from Accounts
union 
select "High Salary" as category,
sum(CASE WHEN income > 50000 THEN 1 ELSE 0 END)AS accounts_count
from Accounts

```

```{r}
library(dplyr)

# Create Accounts data frame
Accounts <- data.frame(
  account_id = c(3, 2, 8, 6),
  income = c(108939, 12747, 87709, 91796)
)

# Categorize salaries and count accounts
result <- Accounts %>%
  mutate(category = case_when(
    income < 20000 ~ 'Low Salary',
    income >= 20000 & income <= 50000 ~ 'Average Salary',
    income > 50000 ~ 'High Salary'
  )) %>%
  group_by(category) %>%
  summarise(accounts_count = n(), .groups = 'drop')
categories <- data.frame(category = c('Low Salary', 'Average Salary', 'High Salary'))
result <- categories %>%
  left_join(result, by = 'category') %>%
  mutate(accounts_count = ifelse(is.na(accounts_count), 0, accounts_count))
```

##

```{sql}

select
case 
    when mod(id,2)!=0 and id+1<= (select count(*)from Seat) then id+1
    when mod(id,2)=0 then id-1
    else id
end as id, 
student
from Seat
order by id asc

```

```{r}
library(dplyr)

# Create Seat data frame
Seat <- data.frame(
  id = c(1, 2, 3, 4, 5),
  student = c("Abbot", "Doris", "Emerson", "Green", "Jeames")
)

# Swap seats of every two consecutive students
result <- Seat %>%
  mutate(id = ifelse(id %% 2 == 1 & id != n(), id + 1, ifelse(id %% 2 == 0, id - 1, id))) %>%
  arrange(id)

# Display the result
print(result)
```


## **1321. Restaurant Growth**

```{sql}
with DailyAmount as(
    select visited_on,
    sum(amount) as amount
    from Customer
    group by visited_on
),
SevenDayWindow as(
    select visited_on,
    sum(amount) over (
        order by visited_on ROWS BETWEEN 6 PRECEDING AND CURRENT ROW ) as amount,
    avg(amount) over(order by visited_on ROWS BETWEEN 6 PRECEDING AND CURRENT ROW ) as average_amount
    from DailyAmount
)
select visited_on, amount, round(average_amount,2) as average_amount 
from SevenDayWindow
where visited_on>=DATE_ADD((select min(visited_on) from Customer),interval 6 day)
order by visited_on;
```

